\bf Title here

### 2020-08-19 paper/paper.Rmd
change the beginning of optimisation lit review

# Derivative free optimisation {#optim}

In modern optimisation problems, gradient information can be hard to evaluate or sometimes even impossible and  Derivative-Free Optimisation (DFO) methods can be useful to approach these problems.
A traditional and still reliable in solving complicated practical problems, is *line search method* [@fletcher2013practical]. In the context of a simple one-dimensional problem of finding the $x$ that minimises $f(x)$, line search achieves the goal via an iterative algorithm in the form of Equation \ref{eq:line-search}.

>>>>

# Optimisation Methods {#optim}

Given an optimisation problem, two basic approaches find the optimum based on different thinking.
An analytical approach aims to find the optimal solution in a finite number of steps, but a potential issue with it is that the close-form solution may not be available when the problem starts to become complex. 
An iterative approach, on the other hand, finds the optimum based on the idea of making progressive improvement to the current solution. An iterative method may end up finding a local optimum but the progressive nature of the algorithm allows the practitioner to decide when to stop if a desirable accuracy has been achieved.

A traditional while often used in practice is an iteartive method called *line search method* [@fletcher2013practical]. In a simple one-dimensional problem of finding the $x$ that minimises $f(x)$, line search achieves the goal via an iterative algorithm in the form of Equation \ref{eq:line-search}.

### 2020-08-19 paper/paper.tex
change the beginning of optimisation lit review

The remainder of the paper is organised as follows. Section \ref{optim}
provides the literature review of optimisation methods, specifically the
line search methods used in projection pursuit guided tour. Section
\ref{tour} reviews projection pursuit guided tour, form the introduces
the optimisation problem, and introduces three main existing algorithms.
Section \ref{vis-diag} presents the new visual diagnostics design, from
forming the data object to the definition of different diagnostic plots.
Section \ref{application} shows some examples of how the diagnostic
plots designed in section \ref{vis-diag} can be applied to understand
and compare different algorithms and how they contribute to
modifications that improve the algorithms. Finally, Section
\ref{implementation} describes the R package: ferrn, that implements all
the visual diagnostics above.

\hypertarget{optim}{%
\section{Derivative free optimisation}\label{optim}}

In modern optimisation problems, gradient information can be hard to
evaluate or sometimes even impossible and Derivative-Free Optimisation
(DFO) methods can be useful to approach these problems. A traditional
and still reliable in solving complicated practical problems, is
\emph{line search method} \citep{fletcher2013practical}. In the context
of a simple one-dimensional problem of finding the \(x\) that minimises
\(f(x)\), line search achieves the goal via an iterative algorithm in
the form of Equation \ref{eq:line-search}.

>>>>

The remainder of the paper is organised as follows. Section \ref{optim}
provides the literature review of optimisation methods, specifically the
line search methods used in projection pursuit guided tour. Section
\ref{tour} reviews projection pursuit guided tour, forms the
optimisation problem, and introduces three main existing algorithms.
Section \ref{vis-diag} presents the new visual diagnostics design, from
forming the data object to the definition of different diagnostic plots
with some small examples. Section \ref{application} shows the
applicaiton of how the diagnostic plots designed in section
\ref{vis-diag} can be used to understand and compare different
algorithms and how they contribute to modifications that improve the
algorithms. Finally, Section \ref{implementation} describes the R
package: ferrn, that implements all the visual diagnostics above.

\hypertarget{optim}{%
\section{Optimisation Methods}\label{optim}}

Given an optimisation problem, two basic approaches find the optimum
based on different thinking. An analytical approach aims to find the
optimal solution in a finite number of steps, but a potential issue with
it is that the close-form solution may not be available when the problem
starts to become complex. An iterative approach, on the other hand,
finds the optimum based on the idea of making progressive improvement to
the current solution. An iterative method may end up finding a local
optimum but the progressive nature of the algorithm allows the
practitioner to decide when to stop if a desirable accuracy has been
achieved.

A traditional while often used in practice is an iteartive method called
\emph{line search method} \citep{fletcher2013practical}. In a simple
one-dimensional problem of finding the \(x\) that minimises \(f(x)\),
line search achieves the goal via an iterative algorithm in the form of
Equation \ref{eq:line-search}.
